%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Emad Aghayi} % Your name
\address{4400 University Drive, MS 4A5, Fairfax, VA 22030} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{ eaghayi@gmu.edu \\ \url{http://mason.gmu.edu/~eaghayi} }
% \\ \url{https://linkedin.com/in/emadaghayi}} % Your phone number and email
%page number
\usepackage{fancyhdr}
\usepackage{lastpage}
\pagestyle{fancy}
\fancyhf{}
\rfoot{Updated \today \hfill Page \thepage \hspace{1pt} of \pageref{LastPage}}
 

\begin{document}

\begin{rSection}{Research Interests}
Software	engineering,	developer	experience	design,	human-computer	interaction,	crowdsourcing


\end{rSection}

% \begin{rSection}{Carrier Objective}
%  To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
% \end{rSection}
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Experience}
{\bf Graduate Research Assistant at \href{https://www2.gmu.edu} {GMU}, Fairfax, VA, USA} \hfill {\em Aug 2017 - Present} 
\\ I am a member of DevX (Software Engineering) lab in which we study the interaction
between users and programming development tools. I work at the intersection of software engineering and human-computer interaction.  My research goal is to make developers more productive by providing better development tools and approaches. To achieve this goal, my research involves understanding developer behaviors, identifying problems, and designing tools and approaches to help with those problems using various HCI methods at each stage. Specifically, I research and design on the crowdsourcing in software engineering.\\
\\{\bf Software Engineer at \href{https://en.isc.co.ir/Portal/Home/}{ISC}, Tehran, Iran} \hfill {\em Dec 2015 - Jul 2017} 
\\ R\&D in the area of large scale software, Leaded development team, built a large scale financial mobile banking software. \\
\\{\bf R\&D Software Engineer at \href{https://www.citydi.com/}{City-DI}, Tehran, Iran} \hfill {\em Apr 2013 - Nov 2015} 
\\ R\&D in software engineering area, Leaded development team, built and maintened multiple software projects in financial industry like BioPay, Dandelion. They are provided with more detail in my personal web-page. \\
\\{\bf Graduate Researcher at \href{https://ut.ac.ir/en} {Network Systems Research Lab , UT,} Tehran, Iran} \hfill {\em Sep 2011 - Feb 2017} 
\\ Researched on wireless networks, remote health monitoring, Smart homes. \\
% \\{\bf Software Developer at Saamaneh Negar Paytakht, Tehran, Iran} \hfill {\em Sep 2010 - Mar 2012} 
% \\ Developed and maintained an Electronic Health Records software. \\


\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf  George Mason University, Fairfax, VA, USA} \hfill {\em Aug 2017 - Present} 
\\ Ph.D. in Computer Science, Department of Computer Science.\\
\\{\bf  George Mason University, Fairfax, VA, USA} \hfill {\em Aug 2017 - May 2020} 
\\ M.Sc. in Software Engineering, Department of Computer Science.\\
\\{\bf University of Tehran (UT), Tehran, Iran } \hfill {\em Aug 2011 - Mar 2014} 
\\ M.Sc. in Information Technology Engineering, Network Science and Technology Group.\\
\\{\bf Shiraz University of Technology, Shiraz, Iran } \hfill {\em Aug 2005 - Jun 2010} 
\\ B.Sc. in Information Technology Engineering, Department of Computer and IT.


\end{rSection}


%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Publications}

\item [{[J1]}]\textbf{E. Aghayi}, T. D. LaToza, P. Surendra, S. Abolghasemi \\  \textit{"Implementing Microservices through Microtasks."}, Submitted to Empirical Software Engineering, 2020.\\
\item [{[J2]}] M. Hoseini, \textbf{E. Aghayi}, F. Saghafi \textit{"A multidimensional model of knowledge sharing behavior in mobile social networks."} Kybernetes, 2018.\\
\item [{[J3]}] S. Majumder, \textbf{E. Aghayi}, M. Noferesti, H. Memarzadeh-Tehran, T. Mondal, Z. Pang, M. Deen \textit{"Smart homes for elderly healthcare—Recent advances and research challenges."}, Sensors, 2017.\\
\item [{[C1]}] Shinobu Saito, Yukako Iimura \textbf{E. Aghayi}, T. D. LaToza \textit{"Does Microtask Programming Work in Industry?"}, Submitted to ICSE 2020 Software Engineering in Practice.\\
\item [{[C2]}] \textbf{E. Aghayi}, M. Khansari, H. Memarzadeh-Tehran \textit{"A new back-off mechanism for the S-MAC protocol with applications in healthcare."} International Symposium on Telecommunications, 2014.
\end{rSection}

\begin{rSection}{Theses} 
\item [{[T1]}]Emad Aghayi. A New Back-off Mechanism for the S-MAC
Protocol.Network Science and Technology Group, University of Tehran. \hfill {\em  2014}
\item [{[T2]}]Emad Aghayi. Various Queue Management Algorithms in TCP,  Department of Computer and IT, Shiraz University of Technology. \hfill {\em  2009}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Academic Services}
{\bf Reviewer:} 
\item CSCW: Journal of Computer Supported Cooperative Work \hfill {\em  2019} 
\item Sensors: journal on the science and technology of sensors and biosensors\hfill {\em  2019}
 \item Kybernetes The international journal of cybernetics, systems and management sciences \hfill {\em  2019}
\item Bioengineering: Journal on the science and technology of bioengineering\hfill {\em  2019}
 \item INTERACT: International Conference on Human-Computer Interaction\hfill {\em  2019}
 
\end{rSection}

\begin{rSection}{Teaching}
{\bf Teaching Assistant,}{ George Mason University, Fairfax, VA, USA} \hfill {\em  2017} 
\\ Course: Object Oriented Programming (CS 211)\\

{\bf Instructor,}{Islamic Azad University, Tehran, Iran} \hfill {\em 2015} 
\\ Course: Introduction to Software Engineering\\

{\bf Instructor,}{Islamic Azad University, Tehran, Iran} \hfill {\em 2015} 
\\ Course: Operating Sysmtes\\

{\bf Instructor,}{Islamic Azad University, Tehran, Iran} \hfill {\em 2015} 
\\ Course: Operating Sysmtes\\

{\bf Teaching Assistant,}{Univeristy of Tehran, Tehran, Iran} \hfill {\em 2014} 
\\ Course: Wireless Sensor Network\\

\end{rSection}

%---------------------------------------------------------------------------
% Awards and Honors
%---------------------------------------------------------------------------
\begin{rSection}{Awards and Honors} 
\item Won the first place among 400 particiapnts in PatriotHacks hackathon \hfill {\em  2019}
\item Graduate Research Assistant, George Mason University, \hfill {\em  Fall 2017 - present}
\item Volgenau School of Engineering Tuition Waiver  \hfill {\em  Fall 2017 - present}
% \item Graduate Teaching Assistant, George Mason University, Fall 2017.
% \item Lecturer, Islamic Azad University, Tehran, Iran, Spring 2015.
\item Travel Grant to attend International Conference on Smart Sensors and Application \hfill {\em  2015}
\item Travel Grant to attend International Symposium on Telecommunications\hfill {\em  2014}
% \item Teaching assistant of wireless sensor network course of graduate student, University of Tehran, 2014.
\item Ranked top 0.16\% among nearly 500,000 participants in Iran’s Physics and Mathematics nationwide universities’ entrance exam. \hfill {\em  2005}
\item Ranked 3rd among more than 5,000 participants taking part in the B.Sc. entrance exam of private university in Iran\hfill {\em  2005} 
\end{rSection}
% ------------------------------------------------------------------------------------------
% Formal Presentation
% ------------------------------------------------------------------------------------------
\begin{rSection}{Formal Presentations}
{\bf International Conference on Smart Sensors and Application,}{ Universiti Teknologi Malaysia, Malaysia ,Kuala Lumpur} \hfill {\em 2015} 
\\ Title: Wirelesss Body Area Networks\\

{\bf International Symposium on Telecommunications,}{ Iran, Tehran} \hfill {\em 2014} 
\\ Title: MAC protocol for WSNs\\

{\bf University of Tehran,}{ Iran, Tehran} \hfill {\em 2014} 
\\ Title: MAC protocol for WSNs\\

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Technical Strengths}

{\bf Back-end:}  {\em Advanced Knowledge of JavaSE, JavaEE, JPA, JTA, JMS, Servlet, Swing, Java Media Framework, Experience with Nodes.js, Express, Python and C\#, Spring (Spring Core, Spring MVC, Spring Boot, Spring Security, Spring Data).} \\
{\bf Front end:}  {\em   JSF, JSP, JavaScript, HTML, CSS, User Experience Testing.}\\
{\bf Containers:}  {\em  Apache tomcat, JBoss EAP, Oracle WebLogic.}\\
{\bf Web-Service:}  {\em  REST (JAX-RS, Jersey), SOAP (JAX-WS, WSDL, Axis2), Spring WS).}\\
{\bf Database:}  {\em Microsoft SQL, Oracle, MySQL, Firebase, Redis.}\\
{\bf Mobile development:}  {\em Android.}\\
{\bf Cloud:}  {\em Google Cloud Functions, Heroku Platform.}\\
{\bf Test:}  {\em Defect and Bug Discovery, Junit, Combinatorial test, Mutation testing (PIT). }\\
{\bf Analyzing and Monitoring:}  {\em SonarQube, SoapUI, JProfiler, Apache JMeter.}\\

\end{rSection}



\end{document}
